---
title: "Technical Conditions"
author: "Dr. Kris Pruitt"
date: "1 March 2023"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(tinytex)
library(corrplot)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(out.width = "60%",fig.align='center')

```

“It contains money transfer and also other gifting goods and service, like you booked a ticket for others, etc.”

TransactionDT: timedelta from a given reference datetime (not an actual timestamp)
“TransactionDT first value is 86400, which corresponds to the number of seconds in a day (60 * 60 * 24 = 86400) so I think the unit is seconds. Using this, we know the data spans 6 months, as the maximum value is 15811131, which would correspond to day 183.”

TransactionAMT: transaction payment amount in USD
“Some of the transaction amounts have three decimal places to the right of the decimal point. There seems to be a link to three decimal places and a blank addr1 and addr2 field. Is it possible that these are foreign transactions and that, for example, the 75.887 in row 12 is the result of multiplying a foreign currency amount by an exchange rate?”

ProductCD: product code, the product for each transaction
“Product isn't necessary to be a real 'product' (like one item to be added to the shopping cart). It could be any kind of service.”

card1 - card6: payment card information, such as card type, card category, issue bank, country, etc.

addr: address
“both addresses are for purchaser
addr1 as billing region
addr2 as billing country”
dist: distance
"distances between (not limited) billing address, mailing address, zip code, IP address, phone area, etc.”
P_ and (R__) emaildomain: purchaser and recipient email domain
“ certain transactions don't need recipient, so R_emaildomain is null.”
C1-C14: counting, such as how many addresses are found to be associated with the payment card, etc. The actual meaning is masked.
“Can you please give more examples of counts in the variables C1-15? Would these be like counts of phone numbers, email addresses, names associated with the user? I can't think of 15.
Your guess is good, plus like device, ipaddr, billingaddr, etc. Also these are for both purchaser and recipient, which doubles the number.”
D1-D15: timedelta, such as days between previous transaction, etc.
M1-M9: match, such as names on card and address, etc.
Vxxx: Vesta engineered rich features, including ranking, counting, and other entity relations.
“For example, how many times the payment card associated with a IP and email or address appeared in 24 hours time range, etc.”
"All Vesta features were derived as numerical. some of them are count of orders within a clustering, a time-period or condition, so the value is finite and has ordering (or ranking). I wouldn't recommend to treat any of them as categorical. If any of them resulted in binary by chance, it maybe worth trying."



First things first lets run correlation matrix to see what variables are colinear with each other in our data set. Please don't crash my computer :).
```{r}
tran_data = read.csv("/Users/zain/Desktop/School/Reg_Proj/ieee-fraud-detection/train_transaction.csv")
identity = read.csv("/Users/zain/Desktop/School/Reg_Proj/ieee-fraud-detection/train_identity.csv")

big_data = merge(x = tran_data, y = identity, by = "TransactionID", all.x = TRUE)

corrplot(cor(big_data))
```



```{r}
tran_data
```